\SdM{Gaia identifies VFTS682 as the most massive, dynamically ejected runaway star known to date}

### 2018-05-11 VFTS682.tex
minor: authors, acknowledgements, color

\usepackage[pagebackref,breaklinks,colorlinks,citecolor=blue]{hyperref}        
\renewcommand*{\backref}[1]{[#1]}  % gives neat back references in the pdf
%\usepackage[%draft, 
%colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{aas_macros}
%\usepackage{amsmath} % clashes with emulateapjj for some reaons
\usepackage[usenames]{xcolor}
\usepackage{comment}
\usepackage{multirow}
%\usepackage{chngpage}
%\usepackage{lscape}
\usepackage{url}
\newcommand{\todo}[1]{{\large $\blacksquare$~\textbf{\color{red}[#1]}}~$\blacksquare$}
\newcommand{\udef}{\stackrel{\mathrm{def}}{=}}
% for tree diagram
%\usepackage{forest}
%\usepackage{tikz-qtree}
%\usetikzlibrary{shadows,trees}

%Selma's comments
\definecolor{Wildstrawberry}{rgb}{1.0, 0.26, 0.64}
\newcommand{\SdM}[1]{{{\color{Wildstrawberry}{#1}}}}
\newcommand{\newtext}[1]{{\color{ForestGreen}\bf{#1}}}

@@

\author{M.~Renzo$^{1}$\and S.~E.~de~Mink$^{1}$ \and \SdM{D.J. Lennon$^{2}$ et al.} \todo{... add coauthors...}%\and
  % S.~Justham\inst{2,3} \and A.~de~Koter\inst{1} \todo{etc..order to be decided}
  .}

\affil{$^{1}$Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands
    $^{2}$ ...
    $^{3}$ ... 
  % \and{School of Astronomy \& Space Science, University of the Chinese
  %   Academy of Sciences, Beijing 100012, China}
  % \and{National Astronomical Observatories, Chinese Academy of
  %   Sciences, Beijing 100012, China}
}

@@

\begin{acknowledgements}
  We are grateful to S.~Torres for extremely useful discussions on the
  Gaia DR2 dataset, and to M.~C.~Ramirez-Tannus for invaluable help.
  The background image of \Figref{fig:main} is based on observations
  made with ESO Telescopes at the La Silla Observatory under programme
  ID 076.C-0888, processed and released by the ESO VOS/ADP group.
  This research made use of APLpy, an open-source plotting package for Python \citep[][]{robitaille:12}.
\end{acknowledgements}
\end{document}

>>>>

\usepackage[pagebackref,breaklinks,colorlinks,citecolor=blue]{hyperref}        
\renewcommand*{\backref}[1]{[#1]}  % gives neat back references in the pdf
%\usepackage[%draft, 
%colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{aas_macros}
%\usepackage{amsmath} % clashes with emulateapjj for some reaons
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{comment}
\usepackage{multirow}
%\usepackage{chngpage}
%\usepackage{lscape}
\usepackage{url}
\newcommand{\todo}[1]{{\large $\blacksquare$~\textbf{\color{red}[#1]}}~$\blacksquare$}
\newcommand{\udef}{\stackrel{\mathrm{def}}{=}}
% for tree diagram
%\usepackage{forest}
%\usepackage{tikz-qtree}
%\usetikzlibrary{shadows,trees}

%Selma's comments
\definecolor{Wildstrawberry}{rgb}{1.0, 0.26, 0.64}
\newcommand{\SdM}[1]{{{\color{Sepia}{#1}}}}
%\renewcommand{\SdM}[1]{{{{#1}}}}

\newcommand{\newtext}[1]{{\color{ForestGreen}\bf{#1}}}

@@

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, \SdM{D.J. Lennon$^{2}$ et al.} \todo{... add coauthors...}%\and
  % S.~Justham\inst{2,3} \and A.~de~Koter\inst{1} \todo{etc..order to be decided}
  .}

\affil{$^{1}$Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands \\
    $^{2}$ ESA, European Space Astronomy Centre, Apdo. de Correos 78, E-28691 Villanueva de la Ca\~nada, Madrid, Spain \\
    $^{3}$ ... 
  % \and{School of Astronomy \& Space Science, University of the Chinese
  %   Academy of Sciences, Beijing 100012, China}
  % \and{National Astronomical Observatories, Chinese Academy of
  %   Sciences, Beijing 100012, China}
}

@@

\begin{acknowledgements}
  We are grateful to S.~Torres for 
  %extremely 
  very useful discussions on the
  Gaia DR2 dataset, and to M.~C.~Ramirez-Tannus for invaluable help.
  \SdM{SdM has received funding under the European Unions Horizon 2020 research and innovation programme from the European Research
Council (ERC) (Grant agreement No. 715063).
   This work has made use of data from the ESA space mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement. }
  The background image of \Figref{fig:main} is based on observations
  made with ESO Telescopes at the La Silla Observatory under programme
  ID 076.C-0888, processed and released by the ESO VOS/ADP group.
  This research made use of APLpy, an open-source plotting package for Python \citep[][]{robitaille:12}.
\end{acknowledgements}
\end{document}
